An elementary and constructive proof of Grothendieck's generic freeness lemma

### 2018-04-17 paper-generic-freeness.tex
typo

We prove Grothendieck's generic freeness lemma for rings and modules in the
following form.

@@

\textbf{Acknowledgments.} The proof presented here was prompted by
user~HeinrichD on MathOverflow~\cite{mo:kernel} and greatly
benefited from discussions with Martin Brandenburg, who needed the constructive
version in paper of him~\cite{brandenburg:schur}. I'm grateful to Marc
Nieper-Wißkirchen for carefully guiding my PhD thesis, where \XXX{...}

>>>>

\noindent
We prove Grothendieck's generic freeness lemma for rings and modules in the
following form.

@@

\textbf{Acknowledgments.} The proof presented here was prompted by
user~HeinrichD on MathOverflow~\cite{mo:kernel} and greatly
benefited from discussions with Martin Brandenburg, who needed the constructive
version in a paper of his~\cite{brandenburg:schur}. I'm grateful to Marc
Nieper-Wißkirchen for carefully guiding my PhD thesis, where \XXX{...}
